% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Zhaohui Ye}

\basicInfo{
  \email{yzhpku@pku.edu.cn} \textperiodcentered\ 
  \phone{(+86) 152-0125-8755} \textperiodcentered\ }

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Peking University (PKU)}, Beijing, China}{2016 -- Present}
\textit{B.S.} in Computer Science (CS), expected March 2020
\\
\textit{GPA: 3.58 / 4.0, Top 30\%} 
\datedsubsection{\textbf{Shaoxing No.1 High School}, Zhejiang, China}{2013 -- 2016}
\textit{High School Education}{}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Practice of Algorithmic Engineer, Deepwise}, Beijing, China}{Summer 2018}
\role{Summer Intern}{}
\role{Key Words: }{Medical Image Processing, First Deep Learning Project}
Brief introduction: 
\begin{itemize}
  \item Exposed to the area of medical image processing and deep learning for the first time.
  \item Planned and implemented a CT series classifier which is now used in the product.
  \item Compressed the classifier's time and memery consumption into a practical scale.
\end{itemize}

\datedsubsection{\textbf{Deecamp Projects, Sinovation Ventures}, Nanjing, China}{Jan. 2019}
\role{Winter Camp}{}
\role{Key Words: }{Quantitative Finance}
Brief introduction:
\begin{itemize}
  \item Implemented a reinforcement learning based model in simulated historical environment of funds.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faUsers\ Course Project}
\datedsubsection{\textbf{Introduction to Natrual Language Processing}}{Nov. 2018}
\role{Key Words: }{Natural Language Processing}
Brief introduction: 
\begin{itemize}
  \item Implemented two models, a seqGAN based peotry generator and an LSTM-CRF based Chinese wordseg model.
  \item Finish two models in two school weeks without knowing GAN or CRF before.
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{Gold Prize}, The ACM-ICPC Asia East Continent League Final }{2017}
\datedline{\textit{Gold Prize}, The ACM-ICPC Asia QingDao Regional Contest }{2017}
\datedline{\textit{Gold Prize}, The ACM-ICPC Asia Xian Regional Contest }{2017}
\datedline{\textit{Gold Prize}, National Olympiad in Informatics }{2015}
\datedline{\textit{First Prize}, National Olympiad in Informatics in Provinces }{2012 - 2016}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C++ == Python > Java
  \item Natural Languages: English - Fluent, Mandarin - Native speaker, The Shaoxing dialect - Native speaker
\end{itemize}


%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
